Forecasting the black Sigatoka development rate: A comparison of machine learning techniques

### 2015-11-24 Paper Sigatoka - 2015.tex
Corregidas unas tildes

The early warning system for black Sigatoka is an adaptation of the yellow Sigatoka warning system developed by Ganry and Meyer and modified by Ganry and Laville to use for controlling yellow Sigatoka in Cameroon. Ternesien and Fouré  later improved Ganry and Laville's system. The latter system is based on weekly observations of disease symtoms on young leaves of the plant, according to Fouré's symptom (stages) descriptions. Arbitrary coefficientes, based on incidence and severity of disease development, are used to calculate two variables: gross sum and state of evolution. Gross sum is based on the stage present and an arbitrary coefficient, which increases with the advance of the symptoms and the juvenility of the leaf. The state of evolution is calculated using the gross sum and the foliar emission period. Although threshold levels were initially suggested as a guide to spray timing, the fluctuation of these two variables was found to better define appropiate times to spray \citep{Marinetal2003}.

@@

which ignores the error if the difference between the prediction value and the actual value is smaller than $ \epsilon$.
The $ \epsilon -insensitive \ loss \ function$ allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability. In SVR, the empirical error is measured by the loss function є-insensitive and the generalization ability is measured by the Euclidean norm of $w$ \citep{XXXX201X}. Then, the optimization problem to identify the regression model can be formulated by \citep{Wei2013}:
\marginnote{Falta completar la cita XXXXX con el libro de SVR}

>>>>

The early warning system for black Sigatoka is an adaptation of the yellow Sigatoka warning system developed by Ganry and Meyer and modified by Ganry and Laville to use for controlling yellow Sigatoka in Cameroon. Ternesien and Four\'e  later improved Ganry and Laville's system. The latter system is based on weekly observations of disease symtoms on young leaves of the plant, according to Four\'e's symptom (stages) descriptions. Arbitrary coefficientes, based on incidence and severity of disease development, are used to calculate two variables: gross sum and state of evolution. Gross sum is based on the stage present and an arbitrary coefficient, which increases with the advance of the symptoms and the juvenility of the leaf. The state of evolution is calculated using the gross sum and the foliar emission period. Although threshold levels were initially suggested as a guide to spray timing, the fluctuation of these two variables was found to better define appropiate times to spray \citep{Marinetal2003}.

@@

which ignores the error if the difference between the prediction value and the actual value is smaller than $\epsilon$.
The $\epsilon -insensitive \ loss \ function$ allows to find the coefficients $w$ and $b$ by solving a convex optimization problem, which balances the empirical error and the generalization ability. In SVR, the empirical error is measured by the loss function є-insensitive and the generalization ability is measured by the Euclidean norm of $w$ \citep{XXXX201X}. Then, the optimization problem to identify the regression model can be formulated by \citep{Wei2013}:
\marginnote{Falta completar la cita XXXXX con el libro de SVR}
